(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-10 table_fpp.tex
fpp table changes

\clearpage
%\LongTables
\begin{deluxetable*}{lcllllllc}
\tablewidth{0pt}
\tabletypesize{\scriptsize}
\tablecaption{False Positive Probability Calculation Results}
\label{Tab:FPP}
\tablehead{
\colhead{EPIC} &
\colhead{Cand. Num.} &
\colhead{max($\delta_{\rm sec}$)} &
\colhead{${\rm Pr}_{\rm EB}$} &
\colhead{${\rm Pr}_{\rm BEB}$} &
\colhead{${\rm Pr}_{\rm HEB}$} &
\colhead{$f_{p}$} &
\colhead{FPP} &
\colhead{Disposition}
}
\startdata
$201208431$ & $1$ & $0.51$ & $< 10^{-4}$ & $0.0058$ & $0.00011$ & $0.22$ & $0.0059$ & Validated \\
$201257461$ & $1$ & $0.59$ & $< 10^{-4}$ & $0.072$ & $0.93$ & $0.22$ & $1$ & FP \\
$201295312$ & $1$ & $0.04$ & $< 10^{-4}$ & $0.008$ & $0.00014$ & $0.15$ & $0.0082$ & Validated \\
$201338508$ & $1$ & $0.63$ & $< 10^{-4}$ & $0.031$ & $0.00063$ & $0.17$ & $0.032$ & Candidate \\
$201338508$ & $2$ & $0.33$ & $< 10^{-4}$ & $0.006$ & $< 10^{-4}$ & $0.17$ & $0.006$ & Validated \\
$201367065$ & $1$ & $0.15$ & $< 10^{-4}$ & $0.01$ & $< 10^{-4}$ & $0.18$ & $0.01$ & Validated \\
$201367065$ & $2$ & $0.67$ & $< 10^{-4}$ & $0.00063$ & $< 10^{-4}$ & $0.14$ & $0.00063$ & Validated \\
$201384232$ & $1$ & $0.44$ & $< 10^{-4}$ & $0.00017$ & $0.00023$ & $0.21$ & $0.0004$ & Validated \\
$201393098$ & $1$ & $0.52$ & $< 10^{-4}$ & $0.02$ & $0.024$ & $0.17$ & $0.044$ & Candidate \\
$201403446$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.0069$ & $0.0013$ & $0.13$ & $0.0083$ & Validated \\
$201445392$ & $1$ & $0.26$ & $< 10^{-4}$ & $0.013$ & $0.053$ & $0.22$ & $0.067$ & Candidate \\
$201445392$ & $2$ & $0.18$ & $< 10^{-4}$ & $0.22$ & $0.048$ & $0.18$ & $0.27$ & Candidate \\
$201465501$ & $1$ & $0.68$ & $< 10^{-4}$ & $0.15$ & $0.0028$ & $0.14$ & $0.15$ & Candidate \\
$201505350$ & $1$ & $2.69$ & $< 10^{-4}$ & $0.13$ & $0.86$ & $0.18$ & $0.99$ & FP \\
$201505350$ & $2$ & $0.70$ & $< 10^{-4}$ & $0.0025$ & $0.00013$ & $0.07$ & $0.0026$ & Validated \\
$201546283$ & $1$ & $0.15$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $< 10^{-4}$ & Validated \\
$201549860$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.013$ & $0.00071$ & $0.20$ & $0.014$ & Candidate \\
$201555883$ & $1$ & $0.94$ & $< 10^{-4}$ & $0.0044$ & $0.0004$ & $0.20$ & $0.0048$ & Validated \\
$201565013$ & $1$ & $1.69$ & $0.0023$ & $0.14$ & $0.82$ & $0.07$ & $0.96$ & FP \\
$201569483$ & $1$ & $2.06$ & $0.48$ & $0.00061$ & $0.097$ & $0.01$ & $0.58$ & Candidate \\
$201577035$ & $1$ & $0.14$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.00015$ & $0.20$ & $0.0002$ & Validated \\
$201596316$ & $1$ & $0.45$ & $< 10^{-4}$ & $0.01$ & $0.0023$ & $0.17$ & $0.013$ & Candidate \\
$201613023$ & $1$ & $0.08$ & $< 10^{-4}$ & $0.0016$ & $< 10^{-4}$ & $0.15$ & $0.0016$ & Validated \\
$201617985$ & $1$ & $0.27$ & $< 10^{-4}$ & $0.12$ & $0.0017$ & $0.16$ & $0.12$ & Candidate \\
$201629650$ & $1$ & $0.43$ & $< 10^{-4}$ & $0.005$ & $0.0012$ & $0.17$ & $0.0062$ & Validated \\
$201635569$ & $1$ & $0.79$ & $< 10^{-4}$ & $0.052$ & $0.071$ & $0.09$ & $0.12$ & Candidate \\
$201649426$ & $1$ & $3.10$ & $0.81$ & $0.0016$ & $0.13$ & $0.01$ & $0.94$ & FP \\
$201702477$ & $1$ & $0.70$ & $< 10^{-4}$ & $0.03$ & $0.29$ & $0.06$ & $0.32$ & Candidate \\
$201736247$ & $1$ & $0.42$ & $< 10^{-4}$ & $0.0015$ & $0.00092$ & $0.22$ & $0.0024$ & Validated \\
$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$ & Candidate \\
$201754305$ & $2$ & $0.38$ & $< 10^{-4}$ & $0.0099$ & $0.00069$ & $0.17$ & $0.011$ & Candidate \\
$201779067$ & $1$ & $1.97$ & $0.034$ & $0.038$ & $0.3$ & $0.03$ & $0.37$ & Candidate \\
$201828749$ & $1$ & $0.39$ & $< 10^{-4}$ & $0.014$ & $0.0024$ & $0.17$ & $0.016$ & Candidate \\
$201855371$ & $1$ & $0.62$ & $< 10^{-4}$ & $0.0006$ & $< 10^{-4}$ & $0.20$ & $0.00071$ & Validated \\
$201912552$ & $1$ & $0.47$ & $< 10^{-4}$ & $0.00058$ & $< 10^{-4}$ & $0.22$ & $0.00058$ & Validated \\
$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.053$ & $0.055$ & $0.05$ & $0.11$ & Candidate

>>>>

\clearpage
%\LongTables
\begin{deluxetable*}{lclccccccc}
\tablewidth{0pt}
\tabletypesize{\scriptsize}
\tablecaption{False Positive Probability Calculation Results}
\label{Tab:FPP}
\tablehead{
\colhead{EPIC} &
\colhead{Cand. Num.} &
\colhead{max($\delta_{\rm sec}$)} &
\colhead{AO?} &
\colhead{${\rm Pr}_{\rm EB}$} &
\colhead{${\rm Pr}_{\rm BEB}$} &
\colhead{${\rm Pr}_{\rm HEB}$} &
\colhead{$f_{p}$} &
\colhead{FPP} &
\colhead{Disposition}
}
\startdata
$201208431$ & $1$ & $0.51$ &  - & $< 10^{-4}$ & $7.4\times10^{-4}$ & $1.0\times10^{-4}$ & $0.22$ & $8.4\times10^{-4}$ & Planet \\
 \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $0.011$  & \color{red}  $0.989$  & \color{red}  $0.22$  & \color{red}  $1.000$  & \color{red}  FP\\
$201295312$ & $1$ & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $1.0\times10^{-4}$ & $0.15$ & $1.1\times10^{-4}$ & Planet \\
$201338508$ & $1$ & $0.63$ &  - & $< 10^{-4}$ & $4.0\times10^{-3}$ & $5.9\times10^{-4}$ & $0.17$ & $4.6\times10^{-3}$ & Planet \\
$201338508$ & $2$ & $0.33$ &  - & $< 10^{-4}$ & $7.7\times10^{-4}$ & $< 10^{-4}$ & $0.17$ & $7.7\times10^{-4}$ & Planet \\
$201367065$ & $1$ & $0.15$ &  - & $< 10^{-4}$ & $1.3\times10^{-3}$ & $< 10^{-4}$ & $0.18$ & $1.3\times10^{-3}$ & Planet \\
$201367065$ & $2$ & $0.67$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.14$ & $< 10^{-4}$ & Planet \\
$201384232$ & $1$ & $0.44$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.1\times10^{-4}$ & $0.21$ & $2.3\times10^{-4}$ & Planet \\
$201393098$ & $1$ & $0.52$ &  - & $< 10^{-4}$ & $2.6\times10^{-3}$ & $0.022$ & $0.17$ & $0.025$ & Candidate \\
$201403446$ & $1$ & $0.18$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $9.8\times10^{-4}$ & $0.13$ & $10.0\times10^{-4}$ & Planet \\
$201445392$ & $1$ & $0.26$ &  - & $< 10^{-4}$ & $1.8\times10^{-3}$ & $0.049$ & $0.22$ & $0.051$ & Candidate \\
$201445392$ & $2$ & $0.18$ &  - & $< 10^{-4}$ & $0.034$ & $0.055$ & $0.18$ & $0.089$ & Candidate \\
$201465501$ & $1$ & $0.68$ &  - & $< 10^{-4}$ & $0.021$ & $3.0\times10^{-3}$ & $0.14$ & $0.025$ & Candidate \\
 \color{red} $201505350$  & \color{red}  $1$  & \color{red}  $2.69$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $0.020$  & \color{red}  $0.966$  & \color{red}  $0.18$  & \color{red}  $0.986$  & \color{red}  FP\\
$201505350$ & $2$ & $0.70$ &  - & $< 10^{-4}$ & $3.0\times10^{-4}$ & $1.2\times10^{-4}$ & $0.07$ & $4.2\times10^{-4}$ & Planet \\
$201546283$ & $1$ & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $< 10^{-4}$ & Planet \\
$201549860$ & $1$ & $0.18$ &  - & $< 10^{-4}$ & $1.7\times10^{-3}$ & $6.5\times10^{-4}$ & $0.20$ & $2.4\times10^{-3}$ & Planet \\
$201555883$ & $1$ & $0.94$ &  - & $< 10^{-4}$ & $5.8\times10^{-4}$ & $3.7\times10^{-4}$ & $0.20$ & $9.5\times10^{-4}$ & Planet \\
 \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}   -  & \color{red}  $2.7\times10^{-3}$  & \color{red}  $0.027$  & \color{red}  $0.926$  & \color{red}  $0.07$  & \color{red}  $0.956$  & \color{red}  FP\\
$201569483$ & $1$ & $2.06$ &  - & $0.468$ & $< 10^{-4}$ & $0.092$ & $0.01$ & $0.560$ & Candidate \\
$201577035$ & $1$ & $0.14$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $1.0\times10^{-4}$ & $0.20$ & $1.1\times10^{-4}$ & Planet \\
$201596316$ & $1$ & $0.45$ &  - & $< 10^{-4}$ & $1.3\times10^{-3}$ & $2.1\times10^{-3}$ & $0.17$ & $3.4\times10^{-3}$ & Planet \\
$201613023$ & $1$ & $0.08$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.15$ & $< 10^{-4}$ & Planet \\
$201617985$ & $1$ & $0.27$ &  - & $< 10^{-4}$ & $0.016$ & $1.7\times10^{-3}$ & $0.16$ & $0.018$ & Candidate \\
$201629650$ & $1$ & $0.43$ &  - & $< 10^{-4}$ & $6.3\times10^{-4}$ & $1.1\times10^{-3}$ & $0.17$ & $1.7\times10^{-3}$ & Planet \\
$201635569$ & $1$ & $0.79$ &  - & $< 10^{-4}$ & $7.5\times10^{-3}$ & $0.069$ & $0.09$ & $0.076$ & Candidate \\
 \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.819$  & \color{red}  $2.2\times10^{-4}$  & \color{red}  $0.119$  & \color{red}  $0.01$  & \color{red}  $0.938$  & \color{red}  FP\\
$201702477$ & $1$ & $0.70$ &  - & $< 10^{-4}$ & $4.0\times10^{-3}$ & $0.277$ & $0.06$ & $0.281$ & Candidate \\
$201736247$ & $1$ & $0.42$ &  - & $< 10^{-4}$ & $1.9\times10^{-4}$ & $8.5\times10^{-4}$ & $0.22$ & $1.0\times10^{-3}$ & Planet \\
$201754305$ & $1$ & $0.65$ &  - & $< 10^{-4}$ & $1.9\times10^{-3}$ & $1.5\times10^{-3}$ & $0.18$ & $3.4\times10^{-3}$ & Planet \\
$201754305$ & $2$ & $0.38$ &  - & $< 10^{-4}$ & $1.2\times10^{-3}$ & $6.4\times10^{-4}$ & $0.17$ & $1.9\times10^{-3}$ & Planet \\
$201779067$ & $1$ & $1.97$ &  - & $0.036$ & $5.0\times10^{-3}$ & $0.286$ & $0.03$ & $0.327$ & Candidate \\
$201828749$ & $1$ & $0.39$ &  - & $< 10^{-4}$ & $1.7\times10^{-3}$ & $2.2\times10^{-3}$ & $0.17$ & $3.9\times10^{-3}$ & Planet \\
$201855371$ & $1$ & $0.62$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $1.7\times10^{-4}$ & Planet \\
$201912552$ & $1$ & $0.47$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet \\
$201929294$ & $1$ & $3.12$ &  - & $< 10^{-4}$ & $6.8\times10^{-3}$ & $0.052$ & $0.05$ & $0.059$ & Candidate
